Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-09-16 doc/tfp_2011_final/main.tex
started revision KK

The distributed computing library presented in this paper is not a
library that helps in parallelizing computations. Rather, it provides
facilities for reliable, distributed execution of parallelizable
computations. In particular, it provides a set of user-friendly APIs
that allows distributed execution of large-scale parallelizable
computations, very relevant to our application needs (and also
relevant to a variety of real-world applications). Further, the
distributed execution could be over multiple cores in the same machine
or over a network of machines. The most important features of our
library are the following:
\begin{itemize}
\item \emph{Genericity}: 
  it allows various patterns of polymorphic computations;
\item \emph{Simplicity}: switching between multiple cores on the same
  machine and a network of machines is as simple as changing a couple
  of lines of code;
\item \emph{Task distribution and fault-tolerance}: 
  it provides automatic task distribution and
  a robust fault-tolerance mechanisms, thereby
  relieving the user from implementing such routines.
\end{itemize}
The application domain of such a distributed computing library is manyfold. 
It serves a variety of users and a wide spectrum of
needs, from desktop PCs to networks of machines.  Typical applications
would involve executing a large number of computation expensive tasks
in a resource-optimal and time-efficient manner. This is also the case
in our research endeavours, that is validating thousands of
verification conditions using automated theorem provers, utilizing the
computing infrastructure to the maximum.
It is worth noting that 
\functory\ is not targeted at applications running on server farms,
crunching enormous amounts of data, such as Google's
MapReduce~\cite{mapreduce}.

>>>>

The distributed computing library presented in this paper is not a
library that helps in parallelizing computations. Rather, it provides
facilities for reliable, distributed execution of parallelizable
computations. In particular, it provides a set of user-friendly APIs
that allows distributed execution of large-scale parallelizable
computations, very relevant to our application needs (and also
relevant to a variety of real-world applications). Further, the
distributed execution could be over multiple cores in the same machine
or over a network of machines. The most important features of our
library are the following:
\begin{itemize}
\item \emph{Genericity}: 
  it allows various patterns of polymorphic computations;
\item \emph{Simplicity}: switching between multiple cores on the same
  machine and a network of machines is as simple as changing a couple
  of lines of code;
\item \emph{Task distribution and fault-tolerance}: 
  it provides automatic task distribution and
  a robust fault-tolerance mechanism, thereby
  relieving the user from implementing such routines.
\end{itemize}
The application domain of such a distributed computing library is manyfold. 
It serves a variety of users and a wide spectrum of
needs, from desktop PCs to networks of machines.  Typical applications
would involve executing a large number of computationally expensive tasks
in a resource-optimal and time-efficient manner. This is also the case
in our research endeavours, that is validating thousands of
verification conditions using automated theorem provers, utilizing the
computing infrastructure to the maximum.
It is worth noting that 
\functory\ is not targeted at applications running on server farms,
crunching enormous amounts of data, such as Google's
MapReduce~\cite{mapreduce}.
